Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-17 article.tex

At first sight, it appears on \textit{Table 1} that partial correlation
methods outperform other methods. Two main reasons may explain this method
hierarchy. First, the quality of the infered network seems related to the
conditioning part of the method. In every method except with partial
correlation, indirect links are confounded with direct links.  Secondly, the
gaussian assumption seems verified and thus linear method appears to be
competitive, e.g. the method correlation already gives good results, with a
non-linear method such as GENIE3.

% Discussion about

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
\toprule
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule
GENIE3                 & & & & & & & & \\
Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

At first sight, it appears on \textit{Table 1} that partial correlation
outperforms other methods. Two main reasons may explain this. First, the
quality of the infered network seems related to the conditioning part of the
method. In every method except with partial correlation, indirect links are
confounded with direct links.  Secondly, the gaussian assumption seems
verified and thus linear method appears to be competitive, e.g. the method
correlation already gives good results, with a non-linear method such as
GENIE3.

% Discussion about the metrics

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
\toprule
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule

Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
GENIE3 (depth = 3)     & & & & & & & & \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\bottomrule
\end{tabular}
\end{table}
